Spring haul-out behavior of seals in the Bering and Chukchi seas

### 2023-09-16 analysis/paper/London_HauloutBeahvior.Rmd
improve title/subtitle/caption
addresses #50

Also removes source col from covariate table

```{r examplePlot, include=TRUE, fig.id="examplePlot", fig.cap="Haul-out behavior observations recorded by a bio-logger deployed on a ribbon seal over two years during the months of March, April, and May. Areas of the plot indicated with an 'X' represent missing data that were not successfully recieved from the tag."}

@@

p <- p + facet_grid(year~month, scales = "free_x")
p <- p + scale_x_continuous(breaks = c(5,15,25), expand = c(0,0)) +
  scale_y_continuous(breaks = c(4,12,20))
p <- p + theme(legend.position = "bottom") +
  theme(strip.background = element_rect(colour="white")) +
  theme(axis.ticks=element_blank()) +
  theme(panel.spacing = unit(0,"line")) +
  ggtitle("Observation records are incomplete because not all data are transmitted",
          subtitle = "percent-dry actogram for a single ribbon seal across two years") +
  xlab("day of month") + ylab("hour (UTC)") 
p <- p + 
  geom_point(aes(x = day, y = hour), data = missing_hours, 
             color = "black", shape = 4, size=0.8)
p
```

@@

covariate_tbl <- tibble::tribble(
  ~Covariate, ~Type, ~Source, ~Description,
  "Age-sex class",   "Categorical", "Field Assessment", 
  "young-of-the-year, subadult, adult male and adult female",
  "Hour", "Continuous; Fourier basis", "Bio-logger", 
  "local solar hour using 6 variables of a Fourier-series basis",
  "Day",   "Continuous", "Bio-logger", 
  "linear, quadratic, and cubic effects of day-of-year",
  "Precip", "Continuous", "NARR", 
  "convective precipitation (ref:kgm2)",
  "Pressure", "Continuous", "NARR", 
  "atmospheric pressure at sea level (kPa)",
  "Temp", "Continuous", "NARR",
  "air temperature (C) at 2m above the earth’s surface",
  "Wind", "Continuous", "NARR", 
  "northerly and easterly vector components for wind converted into a single wind speed via the Euclidean norm",
  "Northing", "Continuous", "Bio-logger","latitude divided by the mean latitude across all locations (for bearded seals only)",
  "Year", "Continuous", "Bio-logger", "For the set of models examining inter-annual variation in sea ice use, we fitted models with the addition of year by day-of-year interactions." 
)

>>>>

```{r examplePlot, include=TRUE, fig.id="examplePlot", fig.cap="Haul-out behavior observations recorded by a bio-logger deployed on a ribbon seal over two years during the months of March, April, and May. This actogram plot represents the transmitted hourly percent-dry values. Areas indicated with an 'X' represent missing data that were not successfully recieved from the tag."}

@@

p <- p + facet_grid(year~month, scales = "free_x")
p <- p + scale_x_continuous(breaks = c(5,15,25), expand = c(0,0)) +
  scale_y_continuous(breaks = c(4,12,20))
p <- p + theme(legend.position = "bottom") +
  theme(strip.background = element_rect(colour="white")) +
  theme(axis.ticks=element_blank()) +
  theme(panel.spacing = unit(0,"line")) +
  ggtitle("Example percent-dry actogram from bio-logger data",
          subtitle = str_wrap("Observation records shown are from a single ribbon seal across a two year deployment. Note that not all records are received from the device.", width = 85)) +
  xlab("day of month") + ylab("hour (UTC)") 
p <- p + 
  geom_point(aes(x = day, y = hour), data = missing_hours, 
             color = "black", shape = 4, size=0.8)
p
```

@@

covariate_tbl <- tibble::tribble(
  ~Covariate, ~Type, ~Description,
  "Age-sex class","Categorical","young-of-the-year, subadult, adult male and adult female",
  "Hour", "Continuous; Fourier basis", "local solar hour using 6 variables of a Fourier-series basis",
  "Day",   "Continuous", "linear, quadratic, and cubic effects of day-of-year",
  "Precip", "Continuous", "convective precipitation (ref:kgm2) (NARR)",
  "Pressure", "Continuous", "atmospheric pressure at sea level (kPa) (NARR)",
  "Temp", "Continuous", "air temperature (C) at 2m above the earth’s surface (NARR)",
  "Wind", "Continuous",
  "northerly and easterly vector components for wind (NARR) converted into a single wind speed via the Euclidean norm",
  "Northing", "Continuous", "latitude divided by the mean latitude across all locations (for bearded seals only)",
  "Year", "Continuous", "For the set of models examining inter-annual variation in sea ice use, we fitted models with the addition of year by day-of-year interactions." 
)
